A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Wrote a paragraph of Strong Normalization

\subsection{Substitution Lemma}

Substitution lemma in \LMD\ is little more complicated than an ordinary one 
because there are six types of judgment and two types of substitution in \LMD.
Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.

@@

\subsection{Inversion Lemma}

@@

Reductions preserve typing.
\begin{theorem}[Preservation]
	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
\end{theorem}

@@

No typed term has an infinite reduction sequence.
\begin{theorem}[Strong Normalization]
	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
\end{theorem}

>>>>

% Substitution Lemma

Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
because there are six types of judgment and two types of substitution in \LMD.
Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.

@@

% Inversion Lemma

@@

% Preservation

Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
Preservation ensure that any one step reduction preserves type.

\begin{theorem}[Preservation]
	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
\end{theorem}

@@

% Strong Normalization

Strong Normalization is also important property which guarantee that
no typed term has an infinite reduction sequence.
We prove this thorem by translating \LMD to Simply Typed Lambda Calculus.

\begin{theorem}[Strong Normalization]
	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
\end{theorem}
